\documentclass[11pt,a4paper]{article}

\usepackage[left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{xcolor}

\hypersetup{
	colorlinks=true,
	linkcolor=black,
	urlcolor=blue
}

\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=2pt}

\titleformat{\section}
{\large\bfseries}
{}
{0em}
{}[\titlerule]

\begin{document}
	
	%================ HEADER =================
	\begin{center}
		{\LARGE \textbf{CHRIS SUNNY THALIYATH}}\\[6pt]
		Robotics \& Autonomous Systems Engineer\\[4pt]
		\href{mailto:chrissunny94@gmail.com}{chrissunny94@gmail.com} $\mid$
		+91-8130324904 $\mid$
		\href{https://www.linkedin.com/in/chris-sunny-thaliyath-02b282365}{LinkedIn} $\mid$
		\href{https://github.com/chrissunny94}{GitHub} $\mid$
		\href{https://www.youtube.com/@ChrisThaliyath153/videos}{YouTube} $\mid$
		\href{https://strava.app.link/nBSLXqC1jWb}{Strava}
	\end{center}
	
	%================ PROFILE =================
	\section*{Profile}
	Robotics software engineer with 7+ years of experience in perception, motion planning, and autonomous systems across ADAS (\href{https://www.mbrdi.co.in}{Mercedes-Benz}), autonomous lawn mowers (\href{https://electricsheeprobotics.com}{Electric Sheep Robotics}), and autonomous golf carts (\href{https://www.boschglobal.com}{Bosch}).  
	Expert in multi-modal perception (camera, LiDAR, radar), SLAM, sensor fusion, 6-DOF pose estimation, and real-time distributed systems.  
	Proficient in Python, C++, PyTorch, ROS/ROS2, and simulation platforms including CARLA, Gazebo, Unity, and Isaac Sim.  
	Driven by continuous reinvention, human-centered technology, and values of peace, empathy, and excellence.
	
	%================ EXPERIENCE =================
	\section*{Experience}
	
	\textbf{\href{https://rosh.ai}{Rosh.ai}} \hfill \textit{Oct 2025 -- Present}\\
	\textit{Lead Engineer – Autonomy}
	
	\begin{itemize}
		\item \textbf{Team Leadership:} Lead a multi-disciplinary team of 10+ engineers; oversee end-to-end development of autonomous vehicle platforms and industrial mobile robotics.
		\item \textbf{Fleet Conversion:} Architected the autonomy stack for converting \textbf{Suzuki Ertiga} and \textbf{Tata Punch} platforms into autonomous shuttles, managing the full transition to drive-by-wire.
		\item \textbf{Brownfield Retrofit:} Design modular hardware and embedded software frameworks for retrofitting legacy vehicle systems with modern autonomous capabilities.
		\item \textbf{Trucking \& Parking:} Technical lead for \textbf{L2/L3 features} in autonomous trucking and a hybrid \textbf{USS + Fisheye} based auto-parking solution for passenger vehicles.
		\item \textbf{Robotic Inspection (Rivian Motors Deployment):} Oversee the development of an autonomous \textbf{Auto-PDI robot} for automating pre-delivery inspections. Deployed on-site at Rivian Motors in Bloomington, IL(OnSite USA) for 5 weeks to conduct quality inspections for End-of-Line (EoL), HVAC, Noise/Vibration/Harshness (NVH), and steering/pedal returnability KPIs.
	    \end{itemize}
    
    \vspace{4pt}
    \vspace{4pt}
	
	\textbf{\href{https://www.mbrdi.co.in}{Mercedes-Benz Research and Development India}} \hfill \textit{Aug 2022 -- Oct 2025 (3.3 Years)}\\
	\textit{Level 3 ADAS – HAF 95 \& HAF 135}
	
	\begin{itemize}
		\item Architected production-ready real-time distributed control modules for L3 ADAS, defining system boundaries, interfaces, and requirements.
		\item Developed LiDAR-based clustering, tracking, and classification pipelines using Euclidean clustering, Hungarian matching, CenterPoint3D, and PointNet for small object detection.
		\item Implemented monocular depth estimation and BEV-based perception models (PyTorch, BEVDet) to replace LiDAR with camera-only occupancy grids.
		\item Hands-on with multi-modal BEVFusion (Camera + LiDAR); explored Vision-Language Models (VLMs) for semantic scene understanding.
		\item Built multi-LiDAR and multi-camera calibration pipelines using ARUCO markers; implemented ICP/NDT-based alignment and ego-motion estimation.
		\item Designed SLAM–IMU–GPS fusion achieving centimeter-level localization accuracy.
		\item Implemented MPC, LQR, Pure Pursuit, and 2-DoF controllers integrated with vehicle dynamics.
		\item Maintained Gen5 ADAS validation pipelines using Airflow, Docker, CI/CD, and large-scale data replay.
		\item Deployed perception and planning stacks on NVIDIA Orin (IDC6) optimized with TensorRT and CUDA.
		\item Developed CAN/CAN-FD drivers, DBC decoding, and ROS interfaces.
	\end{itemize}
	
	\vspace{4pt}
	
	\textbf{\href{https://electricsheeprobotics.com}{Electric Sheep Robotics}} \hfill \textit{July 2021 -- Aug 2022 (1.3 Years)}\\
	\textit{Fully Autonomous Lawn Mowers}
	
	\begin{itemize}
		\item Improved SLAM-based 6-DOF pose estimation using EKF fusion of LiDAR, camera, IMU, and GPS.
		\item Built navigation pipelines across Isaac Sim, Gazebo, and Unity enabling sim-to-real transfer.
		\item Designed synthetic data pipelines for Vision-Language Models.
		\item Integrated Visual Teach \& Repeat (VT\&R) navigation (Prof. Tim Barfoot, University of Toronto).
		\item Deployed autonomy stack on NVIDIA Orin.
	\end{itemize}
	
	\vspace{4pt}
	
	\textbf{\href{https://arway.ai}{Arway.ai}} \hfill \textit{2020}\\
	\textit{Spatial Computing \& AR Platforms}
	
	\begin{itemize}
		\item Implemented kidnapped-robot relocalization using Bag-of-Words techniques.
		\item Cross-compiled ORB-SLAM2 C++ binaries for Unity, Android, and iOS.
		\item Built a custom SLAM-based relocalization system replacing ARKit/ARCore.
	\end{itemize}
	
	\vspace{4pt}
	
	\textbf{\href{https://www.boschglobal.com}{Bosch Global Software Technologies}} \hfill \textit{2020 -- August 2021 (1.1 Years)}\\
	\textit{Senior Software Engineer (Promoted from Software Engineer)}
	
	\begin{itemize}
		\item \textbf{High-Definition Mapping:} Engineered a full-pipeline solution for campus-scale navigation by generating \textbf{Lanelet2} and \textbf{OpenStreetMap (OSM)} compliant maps, enabling lane-level semantic context for autonomous routing.
		\item \textbf{Localization Stack:} Developed and deployed a robust \textbf{LiDAR-SLAM} system utilizing Velodyne VLP-16; implemented multi-sensor \textbf{EKF fusion} (LiDAR + GPS + IMU) to maintain centimeter-level drift-free localization in GPS-denied environments.
		\item \textbf{Extrinsic Calibration:} Designed and implemented automated calibration routines for \textbf{LiDAR-to-LiDAR} and \textbf{LiDAR-to-Camera} setups, ensuring precise point-cloud projection and sensor data alignment for downstream perception.
		\item \textbf{Planning \& Control:} Built waypoint followers and integrated lane-keep assist (LKA) and adaptive cruise control (ACC) logic tailored for low-speed autonomous golf carts.
		\item \textbf{Hardware Integration:} Developed custom ROS drivers for vehicle interfaces (CAN, Electronic Power Steering, throttle/brake) and environmental sensors (Radar, Ultrasonic).
		\item \textbf{Embedded Deployment:} Optimized and deployed the full autonomy stack on \textbf{NVIDIA Drive PX} platforms operating on \textbf{RTOS} (QNX and Linux-RT) to meet safety-critical timing requirements.
	\end{itemize}
	
	\textbf{\href{https://www.boschglobal.com}{Bosch Global Software Technologies}} \hfill \textit{Sept 2018 -- 2020 (1.9 Years)}\\
	\textit{Software Engineer – Autonomous Low-Speed Golf Cart}
	
	\begin{itemize}
		\item \textbf{Drive-by-Wire (DBW) Development:} Developed and integrated ROS-compatible drivers for vehicle actuation systems including \textbf{EPAS (Electronic Power Assisted Steering)}, electronic throttle, and braking systems.
		\item \textbf{Sensor Integration:} Implemented hardware abstraction layers and drivers for a diverse sensor suite: \textbf{Ultrasonic Sensors (USS)}, \textbf{Mid-Range Radar (MRR)}, and \textbf{Wheel Speed Sensors} for odometry.
		\item \textbf{Communication Protocols:} Developed CAN/CAN-FD interfaces and DBC decoding logic to bridge the gap between low-level vehicle controllers and the high-level ROS navigation stack.
		\item \textbf{Control Theory:} Implemented basic waypoint following and PID-based longitudinal/lateral control integrated with vehicle dynamics.
	\end{itemize}\vspace{4pt}
	
	\textbf{\href{https://www.linkedin.com/company/vanora-robots}{Vanora Robots}} \hfill \textit{ June 2017 - 2018 March(1 year)}\\
	\textit{Agricultural Autonomous Robot – Rubber Tapping}
	
	\begin{itemize}
		\item Developed ROS drivers for Sabertooth 2x32 motor controllers on Raspberry Pi.
		\item Programmed embedded controllers (Arduino, STM32) for real-time motor control.
		\item Implemented encoder-based odometry integrated with ROS navigation stack.
		\item Built Visual SLAM pipelines using depth camera (Xbox Kinect) fused with odometry.
		\item Designed ArUco marker–based auto-docking for wireless charging.
	\end{itemize}
	
	%================ EDUCATION =================
	\section*{Education}
	
	\textbf{M.Tech in Artificial Intelligence \& Machine Learning} \hfill \textit{2023 -- 2025}\\
	\href{https://www.iitjammu.ac.in}{Indian Institute of Technology Jammu}
	
	\begin{itemize}
		\item Driver drowsiness detection using Android, DLIB facial landmarks, and CNNs.
		\item End-to-end L3 autonomous vehicle stack using BEV fusion and MPC.
	\end{itemize}
	
	\vspace{4pt}
	
	\textbf{B.Tech in Computer Science} \hfill \textit{2013 -- 2017}\\
	\href{https://snu.edu.in}{Shiv Nadar University}
	
	\begin{itemize}
		\item Built CNC machines, drones, lane-following and self-balancing robots.
		\item Designed Shazam-like audio recognition using FFT-based fingerprints.
		\item Automated greenhouse system using Arduino, Raspberry Pi, OpenCV, and web UI.
	\end{itemize}
	
	%================ SKILLS =================
	\section*{Skills}
	
	\begin{multicols}{2}
		\begin{itemize}
			\item Perception, SLAM, Localization, Mapping
			\item Motion Planning (MPC, LQR, Optimization)
			\item Multi-modal Sensor Fusion
			\item PyTorch, TensorFlow, OpenCV
			\item ROS, ROS2, DDS
			\item Python, C++, CUDA
			\item CARLA, Isaac Sim, Gazebo, Unity
			\item Git, Docker, CI/CD, JIRA, Confluence
		\end{itemize}
	\end{multicols}
	
	%================ PATENTS =================
	\section*{Patents}
	
	\begin{itemize}
		\item \href{https://patents.google.com/patent/DE102024133915A1/en}{DE102024133915A1 – Method and device for reconstructing missing road lanes using LiDAR technology}.  
		Inventors: Patnaikuni Srikhar, Aswathy Radhakrishnan, \textbf{Chris Sunny Thaliyath}.  
		Assignee: Mercedes-Benz Group AG.
	\end{itemize}
	
	%================ AWARDS =================
	\section*{Awards}
	\begin{itemize}
		\item First Place – Lane Following Competition, Galgotias University (2014)
		\item Second Place – Lane Following Competition, IIT Delhi (2015)
		\item Qualified – University Rover Challenge (2017)
		\item Bosch Appreciation – ROS vs Adaptive AUTOSAR Technical Talk
		\item Bosch Appreciation – Top Cycle-to-Work Candidate
	\end{itemize}
	
	%================ LEADERSHIP =================
	\section*{Leadership}
	Head of Robotics Club, Shiv Nadar University (2016–2017).  
	Mentored junior engineers at Bosch and Mercedes-Benz.  
	Leadership philosophy rooted in empathy, truth, and collective growth.
	
	%================ TRAITS =================
	\section*{Personal Traits}
	Curiosity, Integrity, Courage, Empathy, Self-Reflection, Discipline, Patience, Faith, and Love for Humanity.
	
\end{document}
